Bioverse: Origins of Life

### 2023-11-01 src/tex/ms.tex
"signatures", not "markers".

\subsection{Fraction of inhabited planets with detectable biosignatures}
Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of exo-Earth candidates that are both inhabited and harbor detectable biomarkers at the time when we observe them remains speculative; we aggregate them in the unitless parameter $f_\mathrm{life}$.

@@

\section{Exoplanet survey simulations}
\todo[inline]{biomarkers: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biomarker is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
While not the only atmospheric species discussed as a signature for planetary life CITE, we focused on O$_2$ as a representative biomarker for our spectroscopic survey simulations.

@@

>>>>

\subsection{Fraction of inhabited planets with detectable biosignatures}
Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of exo-Earth candidates that are both inhabited and harbor detectable biosignatures at the time when we observe them remains speculative; we aggregate them in the unitless parameter $f_\mathrm{life}$.

@@

\section{Exoplanet survey simulations}
\todo[inline]{biosignatures: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biosignature is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
While not the only atmospheric species discussed as a signature for planetary life CITE, we focused on O$_2$ as a representative biosignature for our spectroscopic survey simulations.

@@

\subsubsection{Diurnal cycles}
\todo[inline]{We assume that tidal locking implies that there are no wet-dry cycles. Challenge this assumption.}
